Windowed Residual-Minimization Model Reduction for Dynamical Systems

### 2019-09-19 main.tex
latest

Simulating parameterized dynamical systems underpins many applications across
science and engineering, including engineering design, control, financial
analysis, and epidemiology. In many contexts, executing a dynamical-system
simulation at a single parameter instance---which entails the numerical
integration of a system of ordinary differential equations (ODEs)---incurs an
extremely large computational expense.  This occurs, for example, when the
state-space dimension is large (e.g., due to fine spatial resolution when
discretizing a partial-differential-equations problem) and/or when the number
of time instances is large (e.g., due to stability or accuracy requirements
that limit the time step).  When the application is time-critical or
many-query in nature, analysts must replace such large-scale parameterized
dynamical-system models with a low-cost approximation that makes the
application tractable.

>>>>

Simulating parameterized dynamical systems underpins many applications across
science and engineering, including engineering design, control, financial
analysis, and epidemiology. In many contexts, executing a dynamical-system
simulation at a single parameter instance---which entails the numerical
integration of a system of ordinary differential equations (ODEs)---incurs an
extremely large computational expense.  This occurs, for example, when the
state-space dimension is large (e.g., due to fine spatial resolution when
discretizing a partial-differential-equation) and/or when the number
of time instances is large (e.g., due to stability or accuracy requirements
that limit the time step).  When the application is time-critical or
many-query in nature, analysts must replace such large-scale parameterized
dynamical-system models with a low-cost approximation that makes the
application tractable.
